---
title: "Simple document"
output: html_document
---

I'm an R Markdown document! 

```{r}
devtools::install_github("p8105/p8105.datasets")

library(p8105.datasets)
library(tidyverse)
library(ggridges)
data(nyc_airbnb)
```


```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  janitor::clean_names() |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location / 2)

view(nyc_airbnb)
```


```{r}
avg_price_borough <- nyc_airbnb |> 
  group_by(borough) |> 
  summarize(avg = mean(price))
```


```{r}
avg_price_neighbourhood <- nyc_airbnb |> 
  group_by(borough, neighbourhood) |> 
  summarize(avg = mean(price))
```


```{r}
str(nyc_airbnb)
```

bronx, brooklyn, manhattan, queens, staten island 
```{r}
avg_price_bronx_n <- nyc_airbnb |> 
  filter(borough == "Bronx") |> 
  group_by(neighbourhood) |> 
  summarize(avg = mean(price))
```


##Brainstorm questions
where are Airbnbs most expensive?
which units have the most availabilty?
how is review score impacted by location?
where are airbnbs? bourgh? neighborhood? lag and long?

#Do somne EDA

```{r}
nyc_airbnb |> 
  count(borough)
```

```{r}
nyc_airbnb |> 
  group_by(borough) |> 
  summarize(mean_price = mean(price))
```

check mean
```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

check median bc it might be skewed distribution 
```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)
```


```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

```{r}
nyc_airbnb |>  
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)
  ) |> 
  arrange(desc(mean_price))
```

distribution of prices across burrows

```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot()
```

ridge plot for visual comparisons
```{r}
nyc_airbnb |> 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan"
  ) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```


## Try to make a map

```{r}
nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
  
```


Try using Leaflet for mapping.

```{r}
library(leaflet)

nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = .5)

```

github documents are static. Leaflet is an interactive file.



